\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-05-29 sections/supplementary_figures.tex
Updates from Overleaf

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS3.pdf}
    \caption{
      \textbf{The distributions of the avergage weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in the synthetic datasets}.
      We observe no significant difference between the various methods on the synthetic datasets used for this study.
    }
    \label{fig:figureS3}
  \end{figure}

  \begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{pdf/all_denoise_reg.pdf}
    \caption{All pairwise correlations comparing the similarity between different denoising and clustering methods}
    \label{fig:figureS4}
  \end{figure}

>>>>

  \begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{figureS3.pdf}
    \caption{
      \textbf{The distributions of the average weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in the synthetic datasets}.
      We observe no significant difference between the various methods on the synthetic datasets used for this study.
    }
    \label{fig:figureS3}
  \end{figure}

%   \begin{figure}[h]
%     \centering
%     \includegraphics[width=0.9\linewidth]{pdf/all_denoise_reg.pdf}
%     \caption*{All pairwise correlations comparing the similarity between different denoising and clustering methods}
%     \label{fig:figureS4}
%   \end{figure}
